Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-11 paper/ijcai16.tex
paper: add missing column.

Second, we want to produce a set of $k$ configurations $\vx^{1}, \ldots,
\vx^{k}$, so that each configuration $\vx^{i}$ is the ``best'' possible
option when evaluated according to the corresponding $\vw^{i}$. Ideally,
this requirement would be implemented as:
%
$$ \vx^{i} = \argmax_{\vx \in \calX_\text{feasible}} \langle \vw^{i}, \vx^{i} \rangle $$
%
However this formulation is highly impractical. We therefore only require 
each option $\vx^{i}$ to be the best {\em among} the various
$\vx^{1}, \ldots, \vx^{k}$. This can be accomplished by imposing
constraints of the form $\langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \geq M$
for all $i,j\in[k]$, $i \ne j$.
This however does not guarantee that the $\vx^{i}$ have a high utility in
absolute terms. We therefore favor high-quality configurations by introducing
an additional term $\sum_{i=1}^k \langle \vw^{i} \vx^{i} \rangle$ in the
objective function. \stefano{sparsity}

>>>>

Second, we want to produce a set of $k$ configurations $\vx^{1}, \ldots,
\vx^{k}$, so that each configuration $\vx^{i}$ is the ``best'' possible
option when evaluated according to the corresponding $\vw^{i}$. Ideally,
this requirement would be implemented as:
%
$$ \vx^{i} = \argmax_{\vx \in \calX_\text{feasible}} \langle \vw^{i}, \vx^{i} \rangle $$
%
However this formulation is highly impractical. We therefore only require 
each option $\vx^{i}$ to be the best {\em among} the various
$\vx^{1}, \ldots, \vx^{k}$. This can be accomplished by imposing
constraints of the form $\langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \geq M$
for all $i,j\in[k]$, $i \ne j$.
This however does not guarantee that the $\vx^{i}$ have a high utility in
absolute terms. We therefore favor high-quality configurations by introducing
an additional term $\sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle$ in the
objective function. \stefano{sparsity}
